Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
review Results
minor changes
Unc example
review conclusions

@@

\caption{Experimental results. \label{tab:results}}
\end{figure}
%---------------------------------

@@

>>>>

\textcolor{red}{Can you relate the benchmarks in Table~\ref{tab:results} in terms of 
$C$ and $G$ as described in section~\ref{experimental-setup}. You could add an additional column to that table.}

@@

\caption{Experimental results. \textcolor{red}{It should be a table and not a figure.} \label{tab:results}}
\end{figure}
%---------------------------------

@@

In this study, we have investigated a CEGIS-based approach that uses inductive synthesis 
in conjunction with a robust closed-loop stability verification algorithm to find a parametric 
solution for a digital controller given a continuous (or discrete) plant specification.
In particular, we have exploited the automatic synthesis of correct-by-construction 
digital controllers along with a model of their physical environment.
We have also modeled a digital equivalent of the physical plant by evaluating the 
effects of the quantisers (A/D and D/A converters) as time discretisation elements 
with quantisation noise. Experimental results show that the inductive back-end of our
CEGIS-based approach is able to synthesise stable controllers in most benchmarks and can be 
complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
Further studies include the extension of this CEGIS-based approach for different classes of systems
({\it e.g.}, state-space) and also consider performance requirements while synthesising 
the digital controller.
